\documentclass{article}

\usepackage{afterpage}
\usepackage{booktabs} % For formal tables
\usepackage{setspace}
\usepackage[multiple]{footmisc}
\usepackage{url}
\usepackage{amsmath,amssymb}
\usepackage{alltt}
%\usepackage{lstlisting}
\usepackage{xspace}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{bbold}
\usepackage{empheq}
\usepackage{tcolorbox}
\usepackage[left=1in,right=1in,top=1.2in,bottom=1.2in,%
            footskip=.5in]{geometry}
%\usepackage[table]{xcolor}
\usepackage{colortbl,hhline}
%\usepackage{pgf}
%\usepackage{pgfplotstable}
\usepackage{multirow}
%\definecolor{lightgreen}{HTML}{90EE90}

\usepackage{amsmath,amsfonts,amsbsy}
\usepackage{fancyvrb,keyval,ifthen}
\usepackage{graphicx}

\usepackage{booktabs}
\usepackage{listings}
\lstset{basicstyle=\ttfamily\footnotesize, frame=single}

\usepackage{paralist}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{titlesec}
\usepackage{balance}
\usepackage{array}

\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
%% %\makeatletter
%% %\renewcommand{\ALG@beginalgorithmic}{\footnotesize}
%% %\makeatother
%% \SetAlFnt{\footnotesize}

%% \usepackage{fancyhdr}


\setlength{\oddsidemargin}{0pt}

\title{CS-3323 Principles of Programming Languages -- Final Exam}

\begin{document}

\date{May 1st -- May 6th, 2020}

\maketitle
{\bf\large
Name: \underline{\mbox{\hspace{4cm}}} 
}
\vspace{2em}

{\bf\large
ID\# \underline{\mbox{\hspace{4cm}}} \hfill
Score: \underline{\mbox{\hspace{4cm}}}
}

\vspace{4em}

\noindent
{\bf Instructions (READ CAREFULLY):}

\begin{itemize}

\item
This exam is worth a total of 30 points. 

\item 
An extra credit question worth 5 points is also included. 

\item You have until May 6th, 6:30pm to upload your solution.

\item You can use books, slides, handouts, and any sort of notes.

\item You can work in groups of up to 3 students, that is, yourself and two more.

\item {\bf All students must upload the same solution by the deadline, both in Gradescope and in Canvas (Final Exam directory at the root of the file space)}.

\item Each student must upload a single PDF file with all the answers. One possible way is printing
a copy of the exam, filling it (either by hand or electronically), and then scanning it. If you don't
have access to a scanner, you can take a picture of each page and then transfer the photos to a computer.
Regardless of the source device (scanner or camera/phone), consolidate all solutions and pages in a single MS WORD file (or similar word editor)
and export it to a PDF format.

\item The estimated time to solve this exam is 4 hours. However, preparing the PDF file with the solutions will likely take time. Please consider the
overhead of scanning/etc in order to submit your exam solutions by the deadline.

\item If you have any question or if something is unclear, email me. 

\item If your question is deemed as a way of luring me to give you a solution to the exam problems, you will be outright ignored.


\end{itemize}

\vspace{2em}

Before proceeding, disclose the students of your group. List their names and student ID (9-digit number):

\begin{tcolorbox}[height=1.5in]

\end{tcolorbox}

\pagebreak

Discussions with peer classmates is encouraged, but your solution can only be
identical to that of the members in your group.  Disclose below the classmates
outside your group (name and ID) with whom you have exchanged opinions,
arguments and/or rationale of solutions for this exam:

\begin{tcolorbox}[height=3in]

\end{tcolorbox}


\vspace{1em}

{\bf Context:}

\begin{itemize}

\item
In programming assignments 3--4 you developed a simple compiler with support for
integer and floating point arithmetic, and basic control-flow constructs.
However, the language and compiler did not support any sort of array data type.

\item
The following exam questions will guide you through the process of adding support
for 1-dimensional integer arrays at both the language level and at the compiler
level.

\item
You can refer to the file grammar.y and all other files of the 3rd and 4th programming assignments for
more precise implementation details. You can find all the files in Canvas.

\item
You are also free to modify the files in order to test that your solution is correct or makes
sense. However, that is not a requirement for getting full credit in the exam.

\end{itemize}


\pagebreak
\input{problem1}

\pagebreak
\input{problem2}


\pagebreak
\input{problem3}

\pagebreak
\input{problem-extra}

\pagebreak


\end{document}
